### 2018-11-06 Sections/cryptowars.tex
Editing Zixin's secs

\section{Attacks on quantum cryptography}

@@

Hacking attacks are related to the weaknesses of the physical implementation, rather than weakness of the theory -- `side-channel attacks'\index{Side-channel attacks}. Some examples of weaknesses which allow zero-error attacks include losses, imperfect components, or correlations between signals leaking information from the system.

When considering the security of noisy channels, one must assume that all noise is due to manipulation by an eavesdropper, the worst-case scenario. An attempted attack is considered successful if it can be proven that the eavesdropper can gain a non-negligible (i.e not exponentially small) amount of mutual information with the final secret-key established between Alice and Bob, without alerting them. Some of the well-known attacks follow:

\subsection{Trojan horse attack}\index{Trojan horse attacks}

The family of Trojan horse attacks involves Eve probing the settings of Alice and Bob by sending light into their devices and collecting the reflected signal. The first one of this kind of attacks actually came for free for the eavesdropper \cite{bib:RevModPhys.81.1301}: it was discovered that some photon-counters emit light when a photon is detected \cite{bib:kurtsiefer2001breakdown}. If the emitted light carries correlated information on which detector was triggered, it must be prevented from leaking outside the secure space and becoming accessible to Eve.

In general, Eve probes into the optical channel that Alice and Bob use to communicate. She send her own states into Alice's system, which will reflect off the same apparatus Alice uses used to encode her signal. Eve's states can be imprinted upon some information about the encoding used by Alice, when Eve measures them. She can then use the result of this measurement, combined with some operation on the Alice's signals to make a best estimate of the quantum state that Alice sent to Bob, thus giving her some non-negligible information mutual with the key\cite{PhysRevA.97.042335}.

@@

A beamsplitting (BS) attack translates the fact that any signal lost over a channel is acquired by Eve. Here Eve induces losses in the communication channel by putting a beamsplitter outside Alice's device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it is therefore always possible for lossy channels, and does not introduce any errors.

>>>>

\section{Attacks on quantum cryptography}\index{Attacks on quantum cryptography}

@@

Hacking attacks in this context exploit weaknesses in the physical implementation, rather than weakness of the theory -- so-called `side-channel attacks'\index{Side-channel attacks}. Some examples of weaknesses which allow zero-error attacks\index{Zero-error attacks} include losses, imperfect components, or correlations between signals leaking information from the system.

When considering the security of noisy channels, one must assume that all noise is due to manipulation by an eavesdropper, the worst-case scenario. An attempted attack is considered successful if it can be proven that the eavesdropper can gain a non-negligible (i.e not exponentially small) amount of mutual information with the final secret-key established between Alice and Bob, without alerting them. Some of the best-known attacks follow:

\subsection{Trojan horse attacks}\index{Trojan horse attacks}

The family of Trojan horse attacks involves Eve probing the settings of Alice and Bob by sending light into their devices and collecting the reflected signal. The first of this kind of attack actually came for free for the eavesdropper \cite{bib:RevModPhys.81.1301}: it was discovered that some photon-counters emit light when a photon is detected \cite{bib:kurtsiefer2001breakdown}. If the emitted light carries correlated information about which detector was triggered, it must be prevented from leaking outside the secure space and becoming accessible to Eve.

In general, Eve probes into the optical channel that Alice and Bob use to communicate. She send her own states into Alice's system, which will reflect off the same apparatus Alice uses used to encode her signal. Eve's states can be imprinted upon some information about the encoding used by Alice, when Eve measures them. She can then use the result of this measurement, combined with some operation on Alice's signals to make a best estimate of the quantum state that Alice sent to Bob, thus giving her some non-negligible mutual information with the key \cite{bib:PhysRevA.97.042335}.

@@

A beamsplitting (BS) attack translates the fact that any signal lost over a channel is acquired by Eve. Here Eve induces losses in the communications channel by putting a beamsplitter outside Alice's device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it is therefore always possible for lossy channels, and does not introduce any errors.

### 2018-11-06 Sections/network_topologies.tex
Editing Zixin's secs

This distribution is observed empirically in many real-world networks and sociological scenarios, and as such is more an observation about the typical behaviour of naturally occurring and evolving human-made networks than an explicit definition for their construction. However, owing to this particular statistical behaviour, and the underlying causations for their Pareto distribution, much has been researched and is known about the properties of scale-free networks.

@@

According to the Bianconi-Barab{\'a}si fitness model\index{Bianconi-Barab{\'a}si fitness model} \cite{bib:BBfitness, bib:BAfitness}, let \mbox{$\eta_i>0$} be the \textit{fitness factor}\index{Fitness factors} of node $i$, which follow a distribution $\rho(\eta)$, characteristic of the network. Then the fitness parameters\index{Fitness parameters} are defined to be normalised such that,
\begin{align}
\Pi_i = \frac{\eta_i k_i}{\sum_j \eta_j k_j}.	
\end{align}
Upon adding a new node of degree $m$ to the network, the temporal dynamics will satisfy,
\begin{align}
\frac{\partial P(k_i)}{\partial t}= m\Pi_i.	
\end{align}
The probability distribution can then be shown to have solution,
\begin{align}
P(k) \approx \int \rho(\eta)\frac{C}{\eta}\left(\frac{m}{k}\right)^\frac{C}{\eta+1}\,d\eta,
\end{align}
where,
\begin{align}
	C &= \int \frac{\rho(\eta)\cdot\eta}{1-\beta(\eta)},\nonumber\\
	\beta(\eta) &= \frac{\eta}{C}.
\end{align}
which is a linear combination of power law relationships, as required for the definition for scale-free.

@@

A feature of scale-free networks of especial interest in the context of computer networks is their robustness against node failure. Suppose we constructed a percolated (Sec.~\ref{sec:perc_topol}) instance of a typical scale-free network. Such a network is highly robust against \textit{random} node/edge deletions compared to many other graph constructions, in the sense that a relatively large number of failures must occur to disconnect the graph. This makes the scale-free network characteristic a particularly attractive one from the perspective of the failure-tolerance of a network. It should be noted that, on the other hand, a scale-free network is highly vulnerable to \textit{targeted} node/edge deletions, that specifically target the highly-connected nodes. A targeted attack against major hubs could disconnect the network with relatively few attacks. This brings with it important geo-strategic\index{Geo-strategic politics} considerations when constructing network infrastructure.

>>>>

This distribution is observed empirically in many real-world networks and sociological structures, and as such is more an observation about the typical behaviour of naturally occurring and evolving human-made networks than an explicit definition for their construction. However, owing to this particular statistical behaviour, and the underlying causations for their Pareto distribution, much has been researched and is known about the properties of scale-free networks.

@@

According to the Bianconi-Barab{\'a}si fitness model\index{Bianconi-Barab{\'a}si fitness model} \cite{bib:BBfitness, bib:BAfitness}, let \mbox{$\eta_i>0$} be the \textit{fitness factor}\index{Fitness factors} of node $i$, which follow a distribution $\rho(\eta)$, a characteristic of the network. Then the fitness parameters\index{Fitness parameters} are defined to be normalised such that,
\begin{align}
\Pi_i = \frac{\eta_i k_i}{\sum_j \eta_j k_j}.	
\end{align}
Upon adding a new node of degree $m$ to the network, the temporal dynamics will satisfy,
\begin{align}
\frac{\partial P(k_i)}{\partial t}= m\Pi_i.	
\end{align}
The probability distribution can then be shown to have solution,
\begin{align}
P(k) \approx \int \rho(\eta)\frac{C}{\eta}\left(\frac{m}{k}\right)^\frac{C}{\eta+1}\,d\eta,
\end{align}
where,
\begin{align}
	C &= \int \frac{\rho(\eta)\cdot\eta}{1-\beta(\eta)},\nonumber\\
	\beta(\eta) &= \frac{\eta}{C},
\end{align}
which is a linear combination of power law relationships, as required for the definition for scale-free.

@@

A feature of scale-free networks of especial interest in the context of computer networks is their robustness against node failure. Suppose we constructed a percolated (Sec.~\ref{sec:perc_topol}) instance of a typical scale-free network. Such a network is highly robust against \textit{random} node/edge deletions compared to many other graph constructions, in the sense that a relatively large number of failures must occur to disconnect the graph. This makes the scale-free network characteristic a particularly attractive one from the perspective of the failure-tolerance of a network. It should be noted that, on the other hand, a scale-free network is highly vulnerable to \textit{targeted} node/edge deletions, that specifically target the highly-connected nodes. A targeted attack against major hubs could disconnect the network with relatively few successful attacks. This brings with it important geo-strategic\index{Geo-strategic politics} considerations when constructing network infrastructure.

### 2018-11-06 Sections/quantum_algorithms.tex
minor
Editing Zixin's secs

As we discuss in Sec.~\ref{sec:NISQ}, we have good reasons to believe that quantum computer
have super-classical abilities. Recently, an unconditional proof of a quantum speed-up has
been shown for a class of circuits.

It is incredibly difficult to compare quantum VS classical polynomial time computation, and 
currently we have noisy gates. Given $n$ qubits, depth $d$, and an error rate $\epsilon$, intuitively, we need the condition
\begin{align}
nd \ll \frac{1}{\epsilon}
\end{align}
\noindent to hold, in order for a quantum algorithm to run successfully. If $d$ is large, then noise dominates and our circuit is classically simulable; on the other hand, if we have a large $n$ and small $d$ (constant depth circuits), we may observe a quantum speed up in the near future. Given these factors, we are motivated to examine shallow circuits. 
Now we will see that there is a distinction between constant depth circuits run using classical VS quantum algorithm.

The result is for the following hidden linear function (HLF) problem \cite{bravyi2018quantum}. Given an 
$n\times n$ symmetric binary matrix $A$, we specify a quadratic form
\begin{align}
q(x) = \vec x^T A \vec x \text{(mod 4)}.
\end{align}
\noindent The goal is to find a binary vector $\vec z \in {0,1}^n$ such that
\begin{align}
q(x) = 2 \vec z^T \vec x
\end{align}
\noindent for all $\vec x$ in the binary null-space of A.

The quantum alvorithm that solves the 2D HLF problem is similar to the Bernstein and Vazirani problem \cite{bernstein1997quantum}. Here a quantum circuit $U_q$ acts on the basis state $\vec x \in \{ 0,1\}^n$
\begin{align}
U_q \ket{x} = i^{q(x)} \ket{x}
\end{align}
The solution is obtained by measuring the state $\ket{\Psi_q}$ in the computational basis,
\begin{align}
\ket{\Psi_q} &= H^{\otimes n }U_q H^{\otimes n} \ket{0}^{\otimes n} \nonumber \\
&= \frac{1}{2^n}\sum_{\vec x,\vec z \in \{ 0,1\}^n} i^{q(x)} (-1)^{\vec z^T x}\ket{z}
\end{align}
\noindent where $H$ is the Hadamard gate. A schematic of the circuit is given in Fig~.\ref{fig:2DHLF}.
Destructive interference between terms in x results a vanishing amplitude
$\braket{z|\Psi_q}=0$ on basis state $\ket{z}$ which are not solutions of the HLF problem.
The circuit $U_q$ can be decomposed into a product of CZ gates and phase-shift gates 
\begin{align}
S_i = \begin{pmatrix}
    1 & 0\\
    0 & -i
    \end{pmatrix} \nonumber
\end{align}

\begin{figure}[!htbp]
%\includegraphics[trim = 0cm 0cm 0cm 0cm, clip, width=1.0\linewidth]{2DHLFcircuit}
\caption{\comment{Insert figure}\label{fig:2DHLF} Quantum circuit to solve the 2D HLF problem. }
\end{figure}

If we lay out the circuit in 2D (hence the 2D HLF problem), it only requires classically controlled Clifford gates between nearest neighbor qubits on a 2D grid. For an example, see Fig.~\ref{fig:2DHLFgrid}.
\begin{figure}[!htbp]
\includegraphics[trim = 0cm 0cm 0cm 0cm, clip, width=0.8\linewidth]{2DHLF_grid}
\caption{\comment{Vector version please}\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid.}
\end{figure}

Now, comparing the quantum algorithm to a classical one, it has been proven that any probabilistic classical circuit with bounded input that solves the 2D HLF problem with high probability $\epsilon \leq 1/8$ must have depth increasing logarithmically with input size \cite{bravyi2018quantum}. The speed-up here is provided by quantum non-locality.

The fact that a problem can be solved with constant depth quantum circuits, but not classical ones shows that there is a clear separation in computational speed between the two cases.

>>>>

As discussed in Sec.~\ref{sec:NISQ}, we have good reason to believe that quantum computers have super-classical capabilities. Recently, an unconditional proof of a quantum speed-up has been shown for a particular class of circuits.

It's incredibly difficult to compare quantum versus classical polynomial time computation, and currently we have noisy gates in the lab. Given $n$ qubits, circuit depth $d$, and an error rate $\epsilon$, intuitively, we demand the condition,
\begin{align}
nd \ll \frac{1}{\epsilon},
\end{align}
to hold, in order for a quantum algorithm to run successfully. If $d$ is large, then noise dominates and our circuit is classically simulable. On the other hand, if we have large $n$ and small $d$ (constant depth circuits), we may observe a quantum speed up in the near future. Given these factors, we are motivated to examine `shallow circuits'. Now we will see that there is a distinction between constant depth circuits run using classical versus quantum algorithm.

The result is for the following hidden linear function (HLF) problem\index{Hidden linear function problem} \cite{bib:bravyi2018quantum}. Given an  \mbox{$n\times n$} symmetric binary matrix $A$, we specify a quadratic form,
\begin{align}
q(x) = \vec x^T A \vec x \text{(mod 4)}.
\end{align}
The goal is to find a binary vector $\vec z \in \{0,1\}^n$ such that,
\begin{align}
q(x) = 2 \vec z^T \vec x,
\end{align}
for all $\vec x$ in the binary null-space of $A$.

The quantum algorithm that solves the 2D HLF problem is similar to the Bernstein-Vazirani problem \cite{bib:bernstein1997quantum}. Here a quantum circuit $U_q$ acts on the basis state $\vec x \in \{ 0,1\}^n$,
\begin{align}
U_q \ket{x} = i^{q(x)} \ket{x}.
\end{align}
The solution is obtained by measuring the state $\ket{\Psi_q}$ in the computational basis. Here,
\begin{align}
\ket{\Psi_q} &= H^{\otimes n }U_q H^{\otimes n} \ket{0}^{\otimes n} \nonumber \\
&= \frac{1}{\sqrt{2^n}}\sum_{\vec x,\vec z \in \{ 0,1\}^n} i^{q(x)} (-1)^{\vec z^T x}\ket{z},
\end{align}
where $H$ is the Hadamard gate. A schematic of the circuit is given in Fig.~\ref{fig:2DHLF}. Destructive interference between terms in $x$ results a vanishing amplitude \mbox{$\braket{z|\Psi_q}=0$} on basis state $\ket{z}$, which are not solutions of the HLF problem. The circuit $U_q$ can be decomposed into a product of CZ gates and phase-shift gates,
\begin{align}
S_i = \begin{pmatrix}
    1 & 0\\
    0 & -i
    \end{pmatrix}.
\end{align}

\begin{figure}[!htbp]
%\includegraphics[clip=true, width=0.475\textwidth]{2DHLFcircuit}
\caption{\comment{Insert figure}\label{fig:2DHLF} Quantum circuit to solve the 2D HLF problem.}
\end{figure}

If we lay out the circuit in 2D (hence the 2D HLF problem), it only requires classically-controlled Clifford gates\index{Clifford gates} between nearest neighbour qubits on a 2D grid. An example is shown in Fig.~\ref{fig:2DHLFgrid}.
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{2DHLF_grid}
\caption{\comment{Vector version please}\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid.}
\end{figure}

Now, comparing the quantum algorithm to a classical one, it has been proven that any probabilistic classical circuit with bounded input that solves the 2D HLF problem with high probability $\epsilon \leq 1/8$ must have depth increasing logarithmically with input size \cite{bib:bravyi2018quantum}. The speed-up here is provided by quantum non-locality\index{Quantum non-locality}.

The fact that a problem can be solved with constant depth quantum circuits, but not classical ones shows that there is a clear exponential computational separation between them.
